---
title: "Northern Alliance of Scotland"
subtitle: "Understanding Poverty and Attainment"  
author: 
  - "CivicDataLab"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    includes:
      after_body: insert-logo.html
    css: xaringan-themer.css
    nature:
      titleSlideClass: [bottom, left]
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
    seal: false
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = TRUE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_mono_light(base_color = "#000000",
                 link_color = "#FF1B70",
                 header_font_google = google_font("Bitter"),
                 text_font_google   = google_font("Avenir", "300", "300i"),
                 code_font_google   = google_font("Fira Mono"))
```

class: left bottom

# Northern Alliance of Scotland

### Using novel data sets and techniques to effectively understand the impact of child poverty on education.

---

## The Project

The aim of this collaboration is to determine what data sources and techniques best reflect the challenges of child poverty, and subsequently provide a means to assess the poverty related attainment gap as a result – which will further allow individual school settings, local authorities and other bodies to plan targeted interventions to reduce it.

Developed through our [Impact Collaborations process](https://www.dataforchildrencollaborative.com/impact-collaborations-1), this project has brought together academic expertise from the Fraser of Allander Institute at the [University of Strathclyde](https://www.strath.ac.uk/business/economics/fraserofallanderinstitute/) and [Glasgow Caledonian University](https://www.gcu.ac.uk/), and data science expertise at [CivicDataLab](https://civicdatalab.in/) and [East Neuk Analytics](https://eastneukanalytics.com/). During this initial phase, the team will work in partnership with [Northern Alliance](https://northernalliance.scot/) and the Local Authorities they represent.

The objective within this initial phase is to work with stakeholders to identify the shared knowledge gap across local authorities, identify the most appropriate indicators and map the suitable data sources that can be used at the school catchment aggregation.


.footnote[**Source**: Understanding Poverty and Attainment Across the Northern Alliance Region of Scotland, Data for Chilren Collaborative; https://www.dataforchildrencollaborative.com/poverty/northern-alliance .]

---

class: left bottom

# Progress Update

---

## Active Threads

.left-column[
### Users
]

.right-column[
#### Understanding The Key Stakeholders

[Survey](https://comms.civicdatalab.in/form/4)
  - Identify what kind of information/data do stakeholders seek/prefer to understand about the needs of children and young people in relation to education in their area.
  - Determine what data sources, tools and techniques best reflect the challenges of child poverty, and subsequently provide a means to assess the poverty related attainment gap as a result.

[Workshop](https://github.com/The-Data-for-Children-Collaborative/noral-user-research/blob/main/research/01-stakeholder-engagement/01.03-workshop.md)  
Information on the following fronts from key stakeholders:
  - Resources and Tools engaged with and their experiences.
  - Feasibility and Impact for possibly shortlisted feature set.
  - Key Experiences and Feedback interacting with related resources.
]

---

## Active Threads

.left-column[
### Users

### Design
]

.right-column[
#### Understanding The Tools

[Design Audit](https://github.com/The-Data-for-Children-Collaborative/noral-design-research/tree/main/design-audit)  
Evaluation Criteria:
  - Previous Product Requirements
  - Stakeholder Interviews or User Surveys
  - Visual Branding Audit
  - Heuristics Evaluation
  - Website & Mobile Analytics
]

---

## Active Threads

.left-column[
### Users

### Design

### Tech
]

.right-column[
#### Exploring Solutions

Identify requirements, challenges, use cases, management procedures and tooling options to [develop and build the features](https://github.com/The-Data-for-Children-Collaborative/noral-tech-research) from the stakeholder workshop.

**Active Research**
  - [Data Collection](https://github.com/The-Data-for-Children-Collaborative/noral-tech-research/tree/main/datacollection)

**Upcoming**
  - Data Stories
  - Information Mapping
  - Comparative Analysis
  - Open Access
  - Capacity Building

]

---

## Upcoming

.pull-left[
#### Users

- User feedback research
- Stakeholder Interviews
- User Personas and Journeys

-----

#### Design

- Existing platforms design review
- User facing tool requirements
- Lo-Fi Wireframes and Feedback
]

.pull-right[
#### Data

- Granularity of data available
- Indicators to be represented
- Sufficiency of the GiS data available

-----

#### Technology

- Technology feature research
- Data architecture suggestions
- Base platform architecture
]

---

## Team

- #### [Akhil Sagiraju](https://civicdatalab.in/team/akhil/); Principal Developer
- #### [Jatin Baghel](https://civicdatalab.in/team/jatin/); Product Designer
- #### [Deepthi Chand](https://civicdatalab.in/team/dc/); Technology Lead
- #### [Arpit Arora](https://civicdatalab.in/team/arpit/); Project Lead

## Resources

- #### [GitHub Repository](https://github.com/The-Data-for-Children-Collaborative/noral-project)
- #### [Project Kanban](https://github.com/orgs/The-Data-for-Children-Collaborative/projects/1)
- #### [Contact E-mail](mailto:education@civicdatalab.in)
